\documentclass{article}

\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
\usepackage{float}

\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}

\setlength\parindent{24pt}

\begin{document}
\begin{titlepage}
	\begin{center}
		\HRule{0.5pt} \\
		\LARGE \textbf{\uppercase{Document plan}}
		\HRule{2pt} \\ [0.5cm]
		{\normalsize \today \par}
		\vspace{2cm}
		\begin{abstract}
			\noindent
			In this document we will shortly describe which student will be doing what, regarding the leftover assignments for the bachelor thesis.
			
			%\keywords{First keyword  \and Second keyword \and Another keyword.}
		\end{abstract}
		\vfill
		\vfill
		{\normalsize Benjamin Vandersmissen \scriptsize benjamin.vandersmissen@student.uantwerpen.be \par}
		{\normalsize Lars Van Roy \scriptsize lars.vanroy@student.uantwerpen.be \par}
		{\normalsize Evelien Daems \scriptsize evelien.daems@student.uantwerpen.be \par}
		{\normalsize Frank Jan Fekkes \scriptsize franciscus.fekkes@student.uantwerpen.be \par}
	\end{center}
	
	\vfill
	
	\date{}
	
	\author{}
\end{titlepage}

\newpage

\tableofcontents

\newpage

\section{introduction}
This document will give a brief description on how we plane to distribute the different assignments, regarding all the assignments that had to be done, and need to be done during this project. The related tests and comments will all be writen by the same student who wrote the code itself.

\section{Simulation Paper}
For the simulation paper, we had the following assignment distribution, and we chose to maintain this distribution for the reevaluation of the paper. Furthermore we will be writing the corresponding entry in the simulation paper, as we assume that you will know best what you did and why you did it, if it was your own assignment: \\
\begin{table}[h!]
\centering
\begin{tabular}{| l | c | r |}
	\hline
	1.1 & Stochastic Variation & Evelien and Lars \\
	\hline
	1.2 & Determining an Extinction threshold & Frank Jan \\
	\hline
	1.3 & Estimating the immunity level & Benjamin \\
	\hline
	1.4 & Estimating R0 & Benjamin \\
	\hline
	2.1 & Investigating the influence of demography on epidemics & Benjamin \\
	\hline
	2.2 & Vaccinating on campus & Frank Jan \\
	\hline
	2.3 & Is commuting to work important for disease spread & Lars \\
	\hline
	3 & Performance profiling of sequential code & Evelien \\
	\hline
\end{tabular}
\caption{distribution of assignments for the Simulation assignment.}
\end{table}
\newpage
\section{Simulator Paper}
For the simulator paper, we distributed the assignments as described in the table below, we also chose to distribute the commenting and writing of tests to the person who made the assignment, as this person is most likely more knowledgeable in the weaknesses of his or her code and will most likely know best which segment does what. We do however intend to look at each others code, even though it might not be our assignment, in order to see whether there are any oversights.
\begin{table}[h!]
	\centering
	\begin{tabular}{| l | c | r |}
		\hline
		1.2.1 & Daycare \& PreSchool & Benjamin \\
		\hline
		1.2.2 & Data formats: json: geogrid & Evelien and Lars \\
		\hline
		1.2.2 & Data formats: json: household & Evelien \\
		\hline
		1.2.2 & Data formats: hdf5 & Benjamin \\
		\hline
		1.2.3 & Data visualisatie & Frank Jan \\
		\hline
		1.2.3 & Data format for visualiser: Proto & Lars\\
		\hline
		1.2.3 & Data format for visualiser: HDF5 & Benjamin \\
		\hline
		1.2.3 & Data format for visualiser: JSON & Frank Jan \\
		\hline
		1.2.4 & Demographic profile & Lars \\
		\hline
		1.2.5 & Grootteklasse personeel van bedrijven & Lars \\
		\hline
		1.2.6 & Simulatie voor Belgi\"e & Evelien \\
		\hline
	\end{tabular}
	\caption{distribution of assignments for the Simulator assignment.}
\end{table}
\section{User Manual}
Finally, the students who wrote the corresponding code, will write the entry for the user manual. The distribution will be as is listed below.
\begin{table}[h!]
	\centering
	\begin{tabular}{| c | r |}
		\hline
		Data visualisatie & Frank Jan \\
		\hline
		data formats: json & Evelien and Lars \\
		\hline
		data formats: hdf5 & Benjamin \\
		\hline
		Demographic Profile & Lars \\
		\hline
		Grootteklasse personeel van bedrijven & Evelien \\
		\hline
	\end{tabular}
	\caption{distribution of assignments for the User Manual.}
\end{table}
\section{Code Documentation}
Every student will write code documentation for their own code, as they have the best view on which segment of the code is written to fulfill which specific query. We will however read and review each others code, to ensure that there are sufficient comments, and that the existing comments are clear.
\section{Conclusion}
As stated in the tables which were provided within this document, we will evenly distribute the assignments between all participating students. We will all write our own related documentation within the code, and within the user manual. Furthermore, we will also write our own tests since the writers will know best what the weakness of their code will or might be. Finally, every student will review one other student's code, as there are often issues which one might not see by themselves.
\end{document}
